Case Study: ChIP-seq Differential Peak Calling (pre-defined regions)

### 2018-03-21 datasets/ChIP-seq/ChIPseq-promoters-h3k4me3.Rmd
Rename chipseq rmds, drop diffbind

```{r}
prom <- promoters(genes(TxDb.Hsapiens.UCSC.hg19.knownGene))
seqlevels(prom, force = TRUE) <- seqlevels(prom)[!grepl("_", seqlevels(prom))]
```

@@

```{r, chipseq-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(dat, pvalue = "pval", covariate = "ind_covariate", maxy = 2)
```

>>>>

```{r}
prom <- promoters(genes(TxDb.Hsapiens.UCSC.hg19.knownGene))
prom <- keepSeqlevels(prom, paste0("chr", c(1:22, "X", "Y", "M")),
                      pruning.mode = "coarse")
```

@@

```{r, chipseq-diag-hist, fig.width=10, fig.height=3.2}
strat_hist(dat, pvalue = "pval", covariate = "ind_covariate",
           maxy = 10)
```
